
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemcol}[2]{\resumeItem{#1}{#2}\vspace{-8pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Sebastián Ignacio Urbina Gajardo}} & Email :  \href{mailto:sebastian.urbina97@gmail.com}{sebastian.urbina97@gmail.com}\\
  \href{https://www.linkedin.com/in/sebaurbina/}{LinkedIn |}
  \href{https://github.com/SebasUrbina}{Github}& Mobile :  +(56)-966719190 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {MSc in Data Science; GPA: 6.7/7.0 }{2023 - 2024}
      \resumeSubHeadingListStart
        \resumeSubItem{}{Relevant Coursework: Natural Language Processing, Deep Learning, Geospatial Data Science, Databases, Data Mining.}
      \resumeSubHeadingListEnd
      \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {BSc in Industrial Engineering; GPA: 6.4/7.0}{2018 - 2024}
      \resumeSubHeadingListStart
        \resumeSubItem{}{Best Graduate of the Year 2024 (1/244)}
        \resumeSubItem{}{Relevant Coursework: Probability and Statistics, Modeling and Optimization, Operations Research, Business Analytics, Marketing II.}
      \resumeSubHeadingListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
    \textbf{Languages:}{ Python, R, JavaScript, TypeScript, HTML, SQL, LaTeX}
     }
 \resumeSubItem{}{
    \textbf{Cloud \& DevOps:}{ AWS (Lambda, ECS, ECR, Step Functions, S3, RDS, DynamoDB, IAM), Docker}
     }
 \resumeSubItem{}{
    \textbf{Technologies and Frameworks:}{ React, FastAPI, Github, Bitbucket.}
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {Data Scientist Senior Specialist (AI Engineer)}{April 2024 - Present}
      \resumeItemListStart
       \resumeItem{}
          {Lead the development of an AI-driven tool that enables business areas to extract insights from unstructured data and generate new metrics to monitor key aspects such as customer satisfaction and adherence.}
        \resumeItem{}
          {Designed a speech-to-text pipeline on AWS (S3, ECS, Lambda, Step Functions), achieving 50x costs compared to closed solutions while maintaining scalability.}
        \resumeItem{}
          {Contributed to the development of a microservices-based RAG architecture using FastAPI, AWS (ECS, Lambda, RDS, DynamoDB), and LangChain.}
        \resumeItem{}
          {Designed and implemented a CI/CD workflow in Bitbucket, automating the deployment of Docker images to Amazon ECR, eliminating manual processes, and significantly improving deployment efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {Data Scientist}{August 2023 - March 2024}
      \resumeItemListStart
        \resumeItem{}
          {Developed a clustering-based anomaly detection system for telecom antennas, identifying more than 50 antennas outliers.}
        \resumeItem{}
          {Developed a novel indicator to quantify customer experience using quality and coverage metrics by processing 100M+ data points in AWS, incorporating geospatial analysis.}
          \resumeItem{}
          {Built a customer segmentation model (Random Forest) based on mobile network quality indicators, reducing data processing by over +90\% through feature selection while maintaining predictive performance.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{}
      {\href{https://github.com/SebasUrbina/poc-openai-agents}{Agentic RAG:} A simple agentic RAG system leveraging the latest OpenAI SDK for agents.}
  \resumeSubItem{}
  {\href{https://github.com/SebasUrbina/expense-tracker-telegram-bot}{Expense Tracker Bot:} Built a serverless Telegram bot using AWS Lambda, DynamoDB, and Google Sheets API to automate expense tracking, handling 1,000+ transactions.}
  \resumeSubHeadingListEnd

%-------CERTIFICATIONS------------------  
\section{Certifications}
\vspace{-15pt}
  \begin{multicols}{2}
    \resumeSubHeadingListStart
    \resumeSubItemcol{Meta}{: Introduction to Front-End Development}
    \resumeSubItemcol{DeepLearning.AI}{: LangChain with Your Data}
    \resumeSubItemcol{Coursera}{: Sequence Models}
    \resumeSubItemcol{Coursera}{: Convolutional Neural Networks}
    \resumeSubItemcol{Huawei}{: Seeds for the future program}
    \resumeSubItemcol{University of Chicago}{: AI and Data Science for Leaders}
  \resumeSubHeadingListEnd
  \end{multicols}
%---------Teaching/Leadership Experience-------
\section{Teaching/Leadership Experience}
 \resumeSubHeadingListStart
  \resumeSubItem
    {Teaching Assistant, University of Chile}
    {; I served as a teaching assistant for the following courses: Data Analysis and Causal Inference, Introduction to Deep Learning, Finance II \& Seminar of Thinking.}
  \resumeSubItem
    {\href{https://ingenieria.uchile.cl/noticias/188882/estudiantes-fcfm-destacaron-en-5ta-version-del-programa-huawei}{Seeds for the Future, Huawei}}
    {; One of the 50 chosen by Huawei to participate in the Seeds for the future program in the creation of technology-based solutions.}
  \resumeSubHeadingListEnd
\end{document}