\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemcol}[2]{\resumeItem{#1}{#2}\vspace{-8pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Patricio Ignacio Dunstan Saez}} & Email :  \href{mailto:patricio.dunstan@gmail.com}{patricio.dunstan@gmail.com}\\
  \href{https://www.linkedin.com/in/patriciodunstan}{LinkedIn} & Mobile :  +(56)-945822142 \\
\end{tabular*}

%-----------PROFILE-----------------
\section{Profile}
\small{
Digital Transformation Leader and Software Developer with Full Stack experience in custom software development and data management. Committed, disciplined, and resilient professional with strong self-learning capacity and adaptability. Values teamwork and feedback to achieve organizational goals.
}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Constructora Harcha}{Los Lagos, Chile}
      {Automation \& Data Developer}{Feb 2025 – Present}
      \resumeItemListStart
        \resumeItem{}{Led the migration of critical modules to a custom platform using \textbf{Flutter, Flask, MySQL}, deployed on \textbf{Google Cloud Run} and \textbf{Firebase}.}
        \resumeItem{}{Implemented a \textbf{CI/CD} process with \textbf{GitHub Actions} to automate software delivery.}
        \resumeItem{}{Established an integrated management system, digitizing key processes (Operations, Sales, Workshop) and generating real-time \textbf{dashboards}.}
        \resumeItem{}{Managed control of key processes (maintenance, sales, fuel) through \textbf{KPIs} tracking, increasing operational efficiency.}
        \resumeItem{}{Generated strategic reports with \textbf{Python}, Excel, and Looker Studio, ensuring data reliability for management decision-making.}
      \resumeItemListEnd

    \resumeSubheading
      {NexIA}{Remote}
      {Software Analyst/Developer}{May 2024 – Dec 2024}
      \resumeItemListStart
        \resumeItem{}{Resolved classified \textbf{bugs} (visual, logic, and service) in \textbf{Angular} frontend and \textbf{Node.js/Express/AWS Lambda} backend under a \textit{serverless} architecture.}
        \resumeItem{}{Developed new modules and functionalities, including view creation, services, and configuration in \textbf{serverless.yml}.}
        \resumeItem{}{Managed infrastructure and deployment using \textbf{Serverless Framework} and monitored performance with \textbf{AWS CloudWatch}.}
        \resumeItem{}{Used \textbf{AWS S3} for temporary document persistence and resolved deployment errors using \textbf{CloudFormation}.}
        \resumeItem{}{Ensured timely delivery of solutions, meeting requirements detailed in \textbf{Jira} tickets.}
      \resumeItemListEnd

    \resumeSubheading
      {Avantgarde}{Santiago, Chile}
      {Software Engineer}{Feb 2024 – May 2024}
      \resumeItemListStart
        \resumeItem{}{Developed real estate management systems using \textbf{Angular 17} and \textbf{NestJS}.}
        \resumeItem{}{Implemented microservices with \textbf{Sequelize ORM} and \textbf{BFF} (Backend for Frontend) with NestJS.}
      \resumeItemListEnd

    \resumeSubheading
      {Desafío Latam}{Remote}
      {Front-End Developer}{Jun 2023 – Sep 2023}
      \resumeItemListStart
        \resumeItem{}{Optimized and updated client's website using \textbf{Next.js, React} and \textbf{Tailwind CSS}.}
        \resumeItem{}{Managed project delivery with \textbf{Jira} and \textbf{Git}, ensuring alignment with client requirements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Talento Digital para Chile}{Chile}
      {Java Developer Program}{Jan 2024 – Jun 2024}
    \resumeSubheading
      {Instituto Profesional IPP}{Chile}
      {Technical Degree in Computer Science}{Sep 2022 – Sep 2024}
    \resumeSubheading
      {Inacap}{Chile}
      {BSc in Mechanical Engineering, Automotive and Electronic Systems}{2007 – 2013}
    \resumeSubheading
      {Adalid Chile}{Chile}
      {DevOps Specialization}{May 2025 – Aug 2025}
  \resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Technical Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{}{\textbf{Languages}{: Python, Java, JavaScript, TypeScript, SQL, HTML, LaTeX.}}
 \resumeSubItem{}{\textbf{Frameworks \& Libraries}{: Angular, Node.js, Express, NestJS, Next.js, Flask, Flutter, Pandas.}}
 \resumeSubItem{}{\textbf{Databases}{: MySQL, PostgreSQL, DynamoDB, MongoDB.}}
 \resumeSubItem{}{\textbf{Cloud Platforms}{: AWS (Lambda, ECS, S3, RDS, IAM, CloudWatch, CodePipeline, CloudFormation), GCP (basic).}}
 \resumeSubItem{}{\textbf{DevOps \& Tools}{: Docker, Serverless Framework, Git, GitHub Actions, Jira, Postman.}}
 \resumeSubItem{}{\textbf{BI \& Analytics}{: Power BI, Looker Studio, Advanced Excel.}}
 \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------------
\section{Certifications}
\vspace{-15pt}
  \begin{multicols}{2}
    \resumeSubHeadingListStart
    \resumeSubItemcol{Power BI}{: Power BI Course}
    \resumeSubItemcol{EF SET}{: English Certificate B2 Upper Intermediate}
    \resumeSubItemcol{Bootcamp}{: Full Stack Java Trainee}
    \resumeSubItemcol{Platzi}{: Programming Fundamentals}
    \resumeSubItemcol{Node.js}{: Node.js Fundamentals}
  \resumeSubHeadingListEnd
  \end{multicols}

%-----------LANGUAGES-----------------
\section{Languages}
 \resumeSubHeadingListStart
 \resumeSubItem{}{\textbf{English:} Professional Working Proficiency (B2).}
 \resumeSubHeadingListEnd

\end{document}