
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemcol}[2]{\resumeItem{#1}{#2}\vspace{-8pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Sebastián Ignacio Urbina Gajardo}} & Email :  \href{mailto:sebastian.urbina97@gmail.com}{sebastian.urbina97@gmail.com}\\
  \href{https://www.linkedin.com/in/sebaurbina/}{LinkedIn |}
  \href{https://github.com/SebasUrbina}{Github}& Mobile :  +(56)-966719190 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {MSc in Data Science; GPA: 6.7/7.0 }{2023 - 2024}
      \resumeSubHeadingListStart
        \resumeSubItem{}{Relevant Coursework: Natural Language Processing, Deep Learning, Geospatial Data Science, Databases, Data Mining.}
      \resumeSubHeadingListEnd
      \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {BSc in Industrial Engineering; GPA: 6.4/7.0}{2018 - 2024}
      \resumeSubHeadingListStart
        \resumeSubItem{}{Oustanding student: 2018, 2019, 2020, 2021 \& 2022.}
        \resumeSubItem{}{Relevant Coursework: Probability and Statistics, Modeling and Optimization, Operations Research, Business Analytics, Marketing II.}
      \resumeSubHeadingListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
    \textbf{Languages}{: Python, R, JavaScript, HTML, SQL, Latex}
     }
 \resumeSubItem{}{
    \textbf{Technologies and Frameworks}{: AWS, Azure, GCP, Github, Bitbucket.}
    }
  \resumeSubItem{}{
    \textbf{Python libraries}{: Numpy, Pandas, Scikit-Learn, Matplotlib, ts-fresh, Seaborn, Wordcloud, Nltk, Spacy, Gensim, Selenium, Scrapy, Boto3, LlamaIndex, LangChain, Streamlit, Keras, Pytorch.}
  }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {Data Scientist Specialist (AI Engineer)}{April 2024 - Present}
      \resumeItemListStart
       \resumeItem{}
          {I actively participated in leading, managing, and defining requirements with various business areas in Generative AI projects.}
          \resumeItem{}
          {Developed and deployed a scalable Speech Analytics application for analyzing audio and text data, leveraging AWS services such as S3 and ECS to ensure efficient processing and storage.}
          \resumeItem{}
          {Built a chatbot using Retrieval-Augmented Generation (RAG) architecture to answer questions based on documents hosted on AWS, leveraging services such as ECS, RDS and Lambda for seamless integration and scalability.}
        \resumeItem{}
         {I developed an end-to-end process in AWS cloud to transcribe audio to text using Deep Learning models, extracting insights from the transcriptions using LLMs.}
      \resumeItemListEnd

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {Data Scientist}{August 2023 - March 2024}
      \resumeItemListStart
        \resumeItem{}
          {Developed a methodology using clustering to identify antennas exhibiting anomalous energy consumption.}
        \resumeItem{}
          {Developed a novel indicator to quantify customer experience using quality and coverage metrics by processing hundreds of millions of data points, incorporating geospatial analysis.}
          \resumeItem{}
          {Trained a random forest model to clasify customers based on quality indicatores of their mobile phone.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
  \resumeSubItem{}
  {\href{https://github.com/SebasUrbina/TextAnalysisProgramaCandidatos2021}{Text Analysis} Text analysis of presidential candidates' programs in the 2021 presidential primaries in Chile.}
  \resumeSubItem{}
  {\href{https://github.com/SebasUrbina/ask-to-me}{Ask-to-me} A Chatbot created in Streamlit to answer questions about my CV using Llama-Index and ChatGPT.}
  \resumeSubItem{}
      {\href{https://github.com/SebasUrbina/whisper-app}{Whisper APP} A streamlit app to utilize the open-source speech-to-text model developed by OpenAI for transcribing audio files.}
  \resumeSubHeadingListEnd

%-------CERTIFICATIONS------------------  
\section{Certifications}
\vspace{-15pt}
  \begin{multicols}{2}
    \resumeSubHeadingListStart
    \resumeSubItemcol{Meta}{: Introduction to Front-End Development}
    \resumeSubItemcol{DeepLearning.AI}{: LangChain with Your Data}
    \resumeSubItemcol{Coursera}{: Sequence Models}
    \resumeSubItemcol{Coursera}{: Convolutional Neural Networks}
    \resumeSubItemcol{Huawei}{: Seeds for the future program}
    \resumeSubItemcol{HardvardX}{: Exercising Leadership: Foundational Principles}
    \resumeSubItemcol{University of Chicago}{: AI and Data Science for Leaders}
    \resumeSubItemcol{Coursera}{: Improving Deep Neural Networks}
    \resumeSubItemcol{Coursera}{: Neural Networks and Deep Learning}
    \resumeSubItemcol{University of Helsinki}{: Certificate of Completition: Elements of IA}
  \resumeSubHeadingListEnd
  \end{multicols}
%---------Teaching/Leadership Experience-------
\section{Teaching/Leadership Experience}
 \resumeSubHeadingListStart
  \resumeSubItem
    {Teaching Assistant, University of Chile}
    {; I served as a teaching assistant for the following courses: Data Analysis and Causal Inference, Introduction to Deep Learning, Finance II \& Seminar of Thinking.}
  \resumeSubItem
    {\href{https://ingenieria.uchile.cl/noticias/188882/estudiantes-fcfm-destacaron-en-5ta-version-del-programa-huawei}{Seeds for the Future, Huawei}}
    {; One of the 50 chosen by Huawei to participate in the Seeds for the future program in the creation of technology-based solutions.}
  \resumeSubItem
    {Neighborhood Secretary, Huapi}
    {; I Served as Secretary of the Neighborhood Association in my residential area.}
  \resumeSubHeadingListEnd
\end{document}