\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemcol}[2]{\resumeItem{#1}{#2}\vspace{-8pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Sebastián Ignacio Urbina Gajardo}} & Email :  \href{mailto:sebastian.urbina97@gmail.com}{sebastian.urbina97@gmail.com}\\
  \href{https://www.linkedin.com/in/sebaurbina/}{LinkedIn |}
  \href{https://github.com/SebasUrbina}{Github} |
  \href{https://sebasurbina.github.io/}{Website}& Mobile :  +(56)-966719190 \\
\end{tabular*}

%----------SUMMARY-----------------
\vspace{8pt}
\noindent
Data Scientist experience in designing, developing, and deploying Traditional/Generative AI solutions in a corporate environment. Skilled in technical leadership, cloud infrastructure, and cross-functional collaboration. Strong background in data science, machine learning, and delivering business value.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {MSc in Data Science; GPA: 6.7/7.0 }{2023 - 2024}
      \resumeSubheading
      {University of Chile}{Santiago, Chile}
      {BSc in Industrial Engineering; GPA: 6.4/7.0}{2018 - 2024}
      \resumeSubHeadingListStart
        \resumeSubItem{Outstanding student: }{2018, 2019, 2020, 2021 \& 2022.}
        \resumeSubItem{Teaching Assistant: }{Data Analysis and Causal Inference, Introduction to Deep Learning, Finance II \& Seminar of Thinking.}
      \resumeSubHeadingListEnd
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
 \resumeSubItem{}{
    \textbf{Languages}{: Python (advanced), R (intermediate), JavaScript (basic), SQL (intermediate)}
     }
 \resumeSubItem{}{
    \textbf{Technologies and Frameworks}{: AWS (intermediate), GCP (basic), Git (advanced)}
    }
 \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {Data Scientist Senior Specialist (AI Engineer)}{April 2025 - Present}
      \resumeItemListStart
        \resumeItem{Ownership of Generative AI products: }
          {Led technical development and iteration of Generative AI solutions, aligning with business goals and delivering continuous value.}
        \resumeItem{Technical solution design: }
          {Defined scalable technical architectures aligned with Entel's corporate Generative AI strategy.}
        \resumeItem{Stakeholder communication: }
          {Prepared and delivered both technical and executive-level presentations to communicate project progress, results, and roadmaps to diverse stakeholders.}

    \resumeItemListEnd

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {Data Scientist Specialist}{April 2024 - March 2025}
      \resumeItemListStart
        \resumeItem{Technical consultancy for internal AI projects: }
          {Acted as technical consultant in Generative AI projects with external vendors, supporting business areas in defining scope and success criteria for AI-based solutions.}
        \resumeItem{POC/MVP development and business insights: }
            {Built MVPs using Generative AI and presented data-driven insights to guide strategic decisions across business areas.}
        \resumeItem{Chatbot with RAG architecture: }
          {Built a chatbot using Retrieval-Augmented Generation (RAG) to answer questions based on internal documentation, leveraging AWS services such as ECS, RDS, and Lambda.}
          \resumeItem{Cloud management: }
          {Managed and deployed cloud infrastructure on AWS, provisioning services, monitoring costs, and supporting the team in adopting new cloud tools and practices.}
      \resumeItemListEnd

    \resumeSubheading
      {Entel}{Santiago, Chile}
      {Data Scientist}{August 2023 - March 2024}
      \resumeItemListStart
        \resumeItem{Anomaly detection: }
          {Developed a methodology using clustering techniques to identify antennas with anomalous energy consumption; 80\% of the identified antennas presented opportunities for energy efficiency improvements.}
        \resumeItem{Customer experience insights: }
          {Created a novel metric to evaluate customer experience by processing hundreds of millions of quality and coverage data points, including geospatial analysis to evaluate customer experience trought network coverage.}
        \resumeItem{Customer segmentation modeling: }
          {Trained a supervised models to classify customers based on quality indicators of mobile phone data.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%TODO: Evaluate how to show my personal projects.
% \section{Projects}
%   \resumeSubHeadingListStart
%   \resumeSubItem{}
%   {\href{https://github.com/SebasUrbina/expense-tracker-telegram-bot}{Expense Tracker Bot:} Designed and implemented a serverless Telegram bot leveraging AWS Lambda, DynamoDB, and the Google Sheets API to automate expense tracking and seamless data updates in Google Sheets.}
%   \resumeSubItem{}
%   {\href{https://github.com/SebasUrbina/ask-to-me}{Ask-to-me:} A Chatbot created in Streamlit to answer questions about my CV using Llama-Index and ChatGPT.}
%   \resumeSubItem{}
%       {\href{https://github.com/SebasUrbina/whisper-app}{Whisper APP:} A streamlit app to utilize the open-source speech-to-text model developed by OpenAI for transcribing audio files.}
%   \resumeSubHeadingListEnd

%-------CERTIFICATIONS------------------  
\section{Certifications}
\vspace{-15pt}
  \begin{multicols}{2}
    \resumeSubHeadingListStart
    \resumeSubItemcol{Meta}{: Version Control}
    \resumeSubItemcol{University of Chicago}{: AI and Data Science for Leaders}
    \resumeSubItemcol{Huawei}{: Seeds for the future program}
    \resumeSubItemcol{HardvardX}{: Exercising Leadership: Foundational Principles}
  \resumeSubHeadingListEnd
  \end{multicols}
%---------Teaching/Leadership Experience-------
%TODO: Look the way to show the following information not extending for more than one page. 
% \section{Teaching/Leadership Experience}
%  \resumeSubHeadingListStart
%   \resumeSubItem
%     {\href{https://ingenieria.uchile.cl/noticias/188882/estudiantes-fcfm-destacaron-en-5ta-version-del-programa-huawei}{Seeds for the Future, Huawei}}
%     {; One of the 50 chosen by Huawei to participate in the Seeds for the future program in the creation of technology-based solutions.}
%   \resumeSubItem
%     {Neighborhood Secretary, Huapi}
%     {; I Served as Secretary of the Neighborhood Association in my residential area.}
%   \resumeSubHeadingListEnd
\end{document}